SunPy - Python for Solar Physics

### 2014-08-26 2-2-Lightcurve.tex
added more instruments that are supported by lightcurve in 0.5

Currently, the \texttt{LightCurve} class is compatible with the
following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.  For each of these instruments, a subclass of the
\texttt{LightCurve} object is initialised
(e.g., \texttt{GOESLightCurve}) which inherits from
\texttt{LightCurve}, but allows instrument-specific functionality to be
included.  Future developments will introduce support for additional
instruments and data products, as well as implementing an interface 
similar to that of \texttt{Map}.  Since there is no established standard
as to how time-series data should be stored and distributed, each SunPy 
\texttt{LightCurve} object subclass provides the ability to download its corresponding 
specific data format in its constructor and parse that file type.

>>>>

Currently, the \texttt{LightCurve} class is compatible with the
following data sources: the \textit{GOES} X-ray Sensor (XRS), the \textit{Nobeyama Radioheliograph (NoRH)}, \textit{PROBA2}/LYRA, \textit{RHESSI}, \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}, and also supports a number of solar summary indices - such as average sunspot number - that are provided by the National Oceanic and Atmospheric Administration (NOAA).  For each of these instruments, a subclass of the
\texttt{LightCurve} object is initialised
(e.g., \texttt{GOESLightCurve}) which inherits from
\texttt{LightCurve}, but allows instrument-specific functionality to be
included.  Future developments will introduce support for additional
instruments and data products, as well as implementing an interface 
similar to that of \texttt{Map}.  Since there is no established standard
as to how time-series data should be stored and distributed, each SunPy 
\texttt{LightCurve} object subclass provides the ability to download its corresponding 
specific data format in its constructor and parse that file type.
